Comparing heatmap functions in R

### 2019-08-11 analysis/paper/Rmd/hotspot-one-chromosome.Rmd
added iheatmapr heatmaps to hotspots-paper.Rmd

@@

```{r, get-allele-effects-{{hot_chr}}}
# add index values for peak position
local_nonlocal_annot <- dplyr::bind_rows(local_annot2, nonlocal_annot) %>%
  mutate(peak_index = match(table = names(map[["{{hot_chr}}"]]), x = marker.id)) %>%
  mutate(peak_effects = purrr::map2(.f = qtl2pleio::get_effects, .x = peak_index, .y = s1coef_out, map = map[["{{hot_chr}}"]])) %>%
  listcol_to_cols(list_column = quo(peak_effects), another_column = quo(symbol))
```

```{r, n-med-{{hot_chr}}, eval = FALSE}
n_med_tr <- 10 # arbitrary threshold for number of mediated traits per local
# only those local traits with n_med_tr or more mediated nonlocal traits 
# appear as annotation columns in the heatmap
n_med_per_local <- med_tib %>%
  group_by(local_symbol) %>%
  filter(lod_diff > 1.5) %>%
  count() %>%
  filter(n >= n_med_tr)
n_med_per_local %>%
  arrange(desc(n)) %>%
  knitr::kable(caption = "Number of mediated traits per local trait for Chr {{hot_chr}} hotspot.")
```

@@

pm[ord, ord] %>% # order both cols and rows by 'ord'
  apply(FUN = trunc2, MARGIN = 2, threshold = 5) %>%
  pheatmap::pheatmap(cluster_rows = FALSE,
                     cluster_cols = FALSE,
                     fontsize = 2,
                     annotation_row = as.data.frame(annfoo)
                     )
```

@@

ggplotly(p)
```

>>>>

```{r, get-allele-effects-{{hot_chr}}}
# add index values for peak position
local_nonlocal_annot <- dplyr::bind_rows(local_annot2, nonlocal_annot) %>%
  mutate(peak_index = match(table = names(map[["{{hot_chr}}"]]), x = marker.id)) %>%
  mutate(peak_effects = purrr::map2(.f = qtl2pleio::get_effects, .x = peak_index, .y = s1coef_out, map = map[["{{hot_chr}}"]])) %>%
  qtl2hotspots::listcol_to_cols(list_column = quo(peak_effects), another_column = quo(symbol))
```

@@

```{r, n-med-{{hot_chr}}}
n_med_tr <- 10 # arbitrary threshold for number of mediated traits per local
# only those local traits with n_med_tr or more mediated nonlocal traits 
# appear as annotation columns in the heatmap
n_med_per_local <- med_tib %>%
  group_by(local_symbol) %>%
  filter(lod_diff > 1.5) %>%
  count() %>%
  filter(n >= n_med_tr)
n_med_per_local %>%
  arrange(desc(n)) %>%
  knitr::kable(caption = "Number of mediated traits per local trait for Chr {{hot_chr}} hotspot.")
```

@@

pm[ord, ord] %>% # order both cols and rows by 'ord'
  apply(FUN = trunc2, MARGIN = 2, threshold = 5) %>%
  pheatmap::pheatmap(cluster_rows = FALSE,
                     cluster_cols = FALSE,
                     fontsize = 2
                     )
```

@@

plotly::ggplotly(p)
```

```{r iheatmapr-{{hot_chr}}}
ann3 <- annots_ord[[3]] %>%
  ungroup() %>%
  select(- symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[3]]$symbol; return(x)})
colnames(ann3) <- LETTERS[1:8]
ann2 <- annots_ord[[2]] %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[2]]$symbol; return(x)})
ann1 <- annots_ord[[1]] %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[1]]$symbol; return(x)})
ann5 <- annots_ord[[5]] %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[5]]$symbol; return(x)})
ann6 <- annots_ord[[6]] %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[6]]$symbol; return(x)})
ann4 <- annots_ord[[4]] %>%
  ungroup() %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[4]]$symbol; return(x)})
mymat <- pm[ord, ord] %>% # order both cols and rows by 'ord'
  apply(FUN = trunc2, MARGIN = 2, threshold = 5)
iheatmapr::main_heatmap(mymat, show_colorbar = FALSE, layout = list(font = list(size = 2))) %>%
  iheatmapr::add_col_labels() %>%
  iheatmapr::add_row_labels() %>%
  iheatmapr::add_col_annotation(ann5) %>%
  iheatmapr::add_main_heatmap(ann3, name = "signal3", size = 0.2, show_colorbar = FALSE) %>%
  iheatmapr::add_main_heatmap(ann2, name = "signal2", size = 0.5, show_colorbar = FALSE) %>%
  iheatmapr::add_main_heatmap(ann1, name = "signal1", size = 0.5, show_colorbar = FALSE) %>%
  iheatmapr::add_row_annotation(ann4) %>%
  iheatmapr::add_row_annotation(ann5, side = "left") %>%
  iheatmapr::add_row_annotation(ann6, side = "left")

```

### 2019-08-11 analysis/paper/preliminary/comparing-heatmaps.Rmd
added iheatmapr heatmaps to hotspots-paper.Rmd

@@

@@

```{r child="methods.Rmd", eval = TRUE}
```

@@

```{r load_heatmaply}
library(heatmaply)
```

```{r saveRDS}
if (!file.exists(here("analysis", "data", "derived_data", "expr.rds"))){
  download.file("https://datadryad.org/bitstream/handle/10255/dryad.166774/Attie_DO378_eQTL_viewer_v1.Rdata?sequence=2",
              destfile = here("analysis", "data", "raw_data", "Attie_DO378_eQTL_viewer_v1.Rdata")
              )
  load(here("analysis", "data", "raw_data", "Attie_DO378_eQTL_viewer_v1.Rdata"))
  saveRDS(dataset.islet.rnaseq$lod.peaks, here("analysis", "data", "derived_data", "lod_peaks.rds"))
  saveRDS(dataset.islet.rnaseq$annots, here("analysis", "data", "derived_data", "annots.rds"))
  saveRDS(dataset.islet.rnaseq$expr, here("analysis", "data", "derived_data", "expr.rds"))
  saveRDS(K, here("analysis", "data", "derived_data", "kinship.rds"))
  saveRDS(map, here("analysis", "data", "derived_data", "map.rds"))
  saveRDS(genoprobs, here("analysis", "data", "derived_data", "genoprobs.rds"))
  saveRDS(dataset.islet.rnaseq$covar, here("analysis", "data", "derived_data", "covar.rds"))
}
```

@@

`r if (eval_code) knitr::knit(text = out[[1]])`

@@

>>>>

# Goals

@@

It's particularly important that I be able to easily annotate, with multiple objects, the rows (and/or columns).

@@

@@

@@

`r knitr::knit(text = out[[1]])`

@@

```{r, eval = FALSE}
devtools::install_github("ropensci/iheatmapr")
```

```{r iheatmapr-{{hot_chr}}}
ann3 <- annots_ord[[3]] %>%
  ungroup() %>%
  select(- symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[3]]$symbol; return(x)})
colnames(ann3) <- LETTERS[1:8]
ann2 <- annots_ord[[2]] %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[2]]$symbol; return(x)})
ann1 <- annots_ord[[1]] %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[1]]$symbol; return(x)})
ann5 <- annots_ord[[5]] %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[5]]$symbol; return(x)})
ann6 <- annots_ord[[6]] %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[6]]$symbol; return(x)})
ann4 <- annots_ord[[4]] %>%
  ungroup() %>%
  select(-symbol) %>%
  as.matrix() %>%
  (function(x){rownames(x) <- annots_ord[[4]]$symbol; return(x)})
mymat <- pm[ord, ord] %>% # order both cols and rows by 'ord'
  apply(FUN = trunc2, MARGIN = 2, threshold = 5)
iheatmapr::main_heatmap(mymat, show_colorbar = FALSE, layout = list(font = list(size = 2))) %>%
  iheatmapr::add_col_labels() %>%
  iheatmapr::add_row_labels() %>%
  iheatmapr::add_col_annotation(ann5) %>%
  iheatmapr::add_main_heatmap(ann3, name = "signal3", size = 0.2, show_colorbar = FALSE) %>%
  iheatmapr::add_main_heatmap(ann2, name = "signal2", size = 0.5, show_colorbar = FALSE) %>%
  iheatmapr::add_main_heatmap(ann1, name = "signal1", size = 0.5, show_colorbar = FALSE) %>%
  iheatmapr::add_row_annotation(ann4) %>%
  iheatmapr::add_row_annotation(ann5, side = "left") %>%
  iheatmapr::add_row_annotation(ann6, side = "left")

```

By using distinct `name` values in the calls to `main_heatmap`, I can get the two heatmaps together and with different color schemes.

```{r sess_info}
devtools::session_info()
```
